\chapter*{Foreword}

This guide is being build with specific kind of dungeon master and player in mind. It introduces a lot of new items and gives players many new options, many of which might even become side quests or elements of story on their own. It only makes sense in a long term game where player characters have some time off from time to time, but not months of free time, in which case refer to the official rules for using craft to earn money.

It is published in hopes that it will be useful but without any real guarantee that it is balanced or that it wont allow players to break certain asumptions about game. I am personaly ok with players winning through tactics and preparation. If that is not your thing then feel free to adapt anything in this guide to your needs.

From the design point of view please note that almost all recepies (except where specificaly written otherwise) use double profficiency. For example making a poison takes nature check with added proficiency for kit. This means that PC with proficiency in both nature and poisoner's kit applies their profficiency bonus twice making it relatively trivial to make poisons on higher levels. This is intentional. Person specialised in certain craft should not have any problems making products of that craft. If you feel like this breakes your game feel free to use basic stat instead of skill used in recepie (\intelligence{} instead of \nature, for example).

Any constructive feedback to this work is more than welcome, feel free to open issue on \url{https://github.com/yoti-dm/sgce/issues/} or send me an email. Same goes for any ideas you would like to contribute. Please keep in mind that this guide is created for a specific game and wont include things specific to any other world or story.  

Word on notation used throughout this work. Creature stats are abbreaviated (\strength, \dexterity, \constitution, \intelligence, \wisdom{} and \charisma), while saving throws get $\diamondsuit$ next to them (\strengthsave, \dexteritysave, \constitutionsave, \intelligencesave, \wisdomsave{} and \charismasave).

Skills are always writen in capitals with main stat in paranthesis. For example deception is displayed as \deception, stealth as \stealth{} and so on.