\chapter*{Appendix A: Feats}

Considerng new powers this guide bestows to tools and how it already grants double proficiencies for most recepies and items, tool related feats needed to be reworked. New feats are also added for those tools that did not have them yet.

\subsubsection{Master alchemist}

You increase your \intelligence{} score by 1 and gain proficiency with alchemy tools.

\subsubsection{Master brewer}

You increase your \wisdom{} score by 1 and gain proficiency with brewer's supplies.

\subsubsection{Master caligrapher}

You increase your \intelligence{} score by 1 and gain proficiency with caligrapher's supplies.

\subsubsection{Master carpenter}

You increase your \strength{} score by 1 and gain proficiency with carpenter's tools.

\subsubsection{Master cartographer}

You increase your \intelligence{} score by 1 and gain proficiency with cartographer's tools.

\subsubsection{Master cobbler}

You increase your \strength{} score by 1 and gain proficiency with cobbler's tools.

\subsubsection{Master cook}

You increase your \wisdom{} score by 1 and gain proficiency with cook's utensils.

\subsubsection{Master of disguise}

You increase your \charisma{} score by 1 and gain proficiency with disguise kit.

\subsubsection{Master forgerer}

You increase your \charisma{} score by 1 and gain proficiency with forgery kit.

\subsubsection{Master glassblower}

You increase your \dexterity{} score by 1 and gain proficiency with glassblower's tools.

\subsubsection{Master herbalist}

You increase your \wisdom{} score by 1 and gain proficiency with herbalism kit.

\subsubsection{Master jeweler}

You increase your \dexterity{} score by 1 and gain proficiency with jeweler's tools.

\subsubsection{Master mason}

You increase your \strength{} score by 1 and gain proficiency with masons's tools.

\subsubsection{Master navigator}

You increase your \intelligence{} score by 1 and gain proficiency with navigator's tools.

\subsubsection{Master painter}

You increase your \wisdom{} score by 1 and gain proficiency with painter's supplies.

\subsubsection{Master of poisons}

You increase your \intelligence{} score by 1 and gain proficiency with poisoner's kit.

\subsubsection{Master potter}

You increase your \dexterity{} score by 1 and gain proficiency with potter's tools.

\subsubsection{Smith's tools}

You increase your \strength{} score by 1 and gain proficiency with smith's tools.

\subsubsection{Master of survival}

You increase your \wisdom{} score by 1 and gain proficiency with survival kit.

\subsubsection{Master thief}

You increase your \dexterity{} score by 1 and gain proficiency with thieve's tools.

\subsubsection{Master thinkerer}

You increase your \intelligence{} score by 1 and gain proficiency with thinker's tools.

\subsubsection{Master weaver}

You increase your \dexterity{} score by 1 and gain proficiency with weaver's tools.

\subsubsection{Master woodcarver}

You increase your \dexterity{} score by 1 and gain proficiency with woodcarver's tools.
