\chapter{Woodcarver's tools}

\section{Items}

\subsection{Arrow shafts}

\subsubsection{Regular arrow shafts}

You can spend 1 hour in an area with appropriate trees to make $$\mathrm{slight\,of\,hands} + \mathrm{profficiency} - 5$$ arrow shafts.

\section{Magical carvings}

\subsubsection{Ear in a tree}

You can spend 10 minutes carving an ear of same size as yours into any wood. Make DC 14 arcana check and add your proficiency if you are proficient with woodcarver's tools. If you succeed ear becomes magical and remains magical for a day or until you carve another ear. While magical you can concentrate for a minute and then your hearing switches to that of an ear. While hearing through the ear in a tree you do not hear with your own ears. You can switch back to your own ears as an action. You do not see or smell through the ear. You can have more than one sense in a tree active

\subsubsection{Eye in a tree}

You can spend 10 minutes carving an eye of same size as yours into any wood. Make DC 15 arcana check and add your proficiency if you are proficient with woodcarver's tools. If you succeed eye becomes magical and remains magical for a day or until you carve another eye. While magical you can concentrate for a minute and then your vision switches to that of an eye. While seeing through the eye in a tree you do not see with your own eyes. You can switch back to your own eyes as an action. You do not hear or smell through the eye.

\subsubsection{Nose in a tree}

You can spend 10 minutes carving a nose of same size as yours into any wood. Make DC 13 arcane check and add your proficiency if you are proficient with woodcarver's tools. If you succeed nose becomes magical and remains magical for a day or until carve another nose. While magical you can concentrate for a minute and then your smell switches to that of an nose. While smelling through the nose in a tree you do not smell with your own nose. You can switch back to your own nose as an action. You do not hear or see through the nose.

\subsubsection{Miscellaneous}

\subsubsection{Wooden doll}

You can spend half an hour working on a small wooden dool that children love. DC 13 sleight of hand + profficiency with tools check to succeed. Materials for the doll can be passively gathered in any woodland area.
